Enhancement of SDR in Thessaloniki

### 2024-08-29 GHI_enh_03_process.tex
Commit 2024-08-27 00:14
Commit 2024-08-27 14:14
Commit 2024-08-28 13:11
Commit 2024-08-28 19:23
Commit 2024-08-29 18:14

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-08-26}

@@

\begin{verbatim}
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
-72.8133 -27.4717   0.7634   0.4285  28.2424  83.4876 
\end{verbatim}

@@

Residuals:
    Min      1Q  Median      3Q     Max 
-316.47 -148.10  -55.61  103.32  718.33

Coefficients:
                  Estimate Std. Error t value Pr(>|t|)   
(Intercept)      1.520e+02  4.805e+01   3.164  0.00169 **
as.numeric(Date) 1.205e-07  3.816e-08   3.157  0.00173 **
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 197.8 on 354 degrees of freedom
Multiple R-squared:  0.02738,   Adjusted R-squared:  0.02463 
F-statistic: 9.966 on 1 and 354 DF,  p-value: 0.001732
\end{verbatim}

@@

Residuals:
    Min      1Q  Median      3Q     Max 
-316.47 -148.10  -55.61  103.32  718.33

Coefficients:
                   Estimate Std. Error t value Pr(>|t|)   
(Intercept)       1.520e+02  4.805e+01   3.164  0.00169 **
ST_E_monthly$Date 1.205e-07  3.816e-08   3.157  0.00173 **
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 197.8 on 354 degrees of freedom
Multiple R-squared:  0.02738,   Adjusted R-squared:  0.02463 
F-statistic: 9.966 on 1 and 354 DF,  p-value: 0.001732
\end{verbatim}

@@

\begin{verbatim}
2024-08-26 19:50:18.2 athan@sagan GHI_enh_03_process.R 3.387402 mins
\end{verbatim}

>>>>

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-08-29}

@@

\begin{verbatim}
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
-72.8133 -27.4712   0.7647   0.4304  28.2448  83.4876 
\end{verbatim}

@@

Residuals:
    Min      1Q  Median      3Q     Max 
-317.54 -148.95  -56.71  107.07  717.24

Coefficients:
                  Estimate Std. Error t value Pr(>|t|)   
(Intercept)      1.533e+02  4.805e+01   3.190  0.00155 **
as.numeric(Date) 1.203e-07  3.816e-08   3.153  0.00175 **
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 197.8 on 354 degrees of freedom
Multiple R-squared:  0.02732,   Adjusted R-squared:  0.02457 
F-statistic: 9.943 on 1 and 354 DF,  p-value: 0.001752
\end{verbatim}

@@

Residuals:
    Min      1Q  Median      3Q     Max 
-317.54 -148.95  -56.71  107.07  717.24

Coefficients:
                   Estimate Std. Error t value Pr(>|t|)   
(Intercept)       1.533e+02  4.805e+01   3.190  0.00155 **
ST_E_monthly$Date 1.203e-07  3.816e-08   3.153  0.00175 **
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 197.8 on 354 degrees of freedom
Multiple R-squared:  0.02732,   Adjusted R-squared:  0.02457 
F-statistic: 9.943 on 1 and 354 DF,  p-value: 0.001752
\end{verbatim}

@@

\begin{verbatim}
2024-08-29 10:26:26.0 athan@sagan GHI_enh_03_process.R 3.652528 mins
\end{verbatim}

### 2024-08-29 GHI_enh_04_investigate.tex
Commit 2024-08-27 00:14
Commit 2024-08-27 14:14
Commit 2024-08-28 13:11
Commit 2024-08-28 19:23
Commit 2024-08-29 18:14

\begin{verbatim}
Warning: Removed 27787 rows containing non-finite outside the scale range
(`stat_bin()`).
\end{verbatim}

@@

\begin{verbatim}
Warning: Removed 246 rows containing non-finite outside the scale range
(`stat_bin()`).
Removed 27787 rows containing non-finite outside the scale range
(`stat_bin()`).
\end{verbatim}

@@

lmY: 116.8672 +/- 33.89196

@@

lmY: 45.58799 +/- 10.96835

@@

lmY: 0.029427 +/- 0.054286

@@

lmY: 0.03518 +/- 0.042507

@@

lmY: 116.3147 +/- 30.85223

@@

lmY: 45.55073 +/- 10.16657

@@

\begin{verbatim}
2024-08-26 19:52:09.6 athan@sagan GHI_enh_04_investigate.R 0.838254 mins
\end{verbatim}

>>>>

\begin{verbatim}
Warning: Removed 27907 rows containing non-finite outside the scale range
(`stat_bin()`).
\end{verbatim}

@@

\begin{verbatim}
Warning: Removed 246 rows containing non-finite outside the scale range (`stat_bin()`).
Removed 27907 rows containing non-finite outside the scale range (`stat_bin()`).
\end{verbatim}

@@

lmY: 116.2574 +/- 34.09971

@@

lmY: 45.56418 +/- 10.97738

@@

lmY: 0.025809 +/- 0.054193

@@

lmY: 0.034753 +/- 0.043154

@@

lmY: 115.7198 +/- 31.03115

@@

lmY: 45.48822 +/- 10.14071

@@

\begin{verbatim}
2024-08-29 10:27:28.5 athan@sagan GHI_enh_04_investigate.R 0.869041 mins
\end{verbatim}
